Studying the Performance of the Jellyfish Search Optimiser for the Application of Projection Pursuit

### 2024-07-24 jso.qmd
add definition for proj distance and squintability

@@

Let $A \in \mathbf{R}^{p \times d}$ be the d-D projection basis and
$A^*$ be the optimal basis achieving the maximum index value for a given
projection pursuit problem defined by the shape to find, data dimension,
and the index function $f(.)$. The projection distance $d(A, A^*)$, is
defined as the Frobenius norm $\lVert . \rVert _F$, between the squared
difference of these two bases:

$$d(A, A^*) = \lVert M \rVert _F = \sum_{ij} M_{ij}^2, \text{ where } M = AA^\prime - A^*A^{*\prime}\ .$$ {#eq-proj-dist}

>>>>

\begin{defn}\label{def:proj-dist}
Let $A \in \mathbf{R}^{p \times d}$ be the d-dimensional projection basis and
$A^*$ be the optimal basis that achieves the maximum index value for a given
PP problem defined by the shape to find, data dimension,
and the index function. The projection distance $d(A, A^*)$ between $A$ 
and $A^*$ is defined as 
$d(A, A^*) = \lVert AA^\prime - A^*A^{*\prime}\  \rVert _F$
where $\lVert . \rVert _F$ denotes the Frobenius norm, given by
$\lVert M \rVert _F = \sqrt{\sum_{ij} M_{ij}^2}$. 
\end{defn}

\begin{defn}\label{def:squintability}
Let $g$ be the function that maps the projection distance, $d = d(A, A^*)$, 
to the index value $f(XA)$, such that $g(d(A, A^*)) = f(XA)$.
The squintability of $f(\cdot)$, denoted $\varsigma(f)$, is defined as 
$$\varsigma(f) = c \times \max_{d} \Delta g(d) \times \arg \max_{d}  \Delta g(d)$$ 
where $c$ is a constant scaling factor, $\max_A \Delta g(x)$ represents the 
maximum change in the index value along the curve $g$, and $\arg \max_{d} \Delta g(x)$ represents the projection distance at which this largest gradient is attained.

\end{defn}
Definition \ref{def:squintability} is ...

@@

### 2024-07-24 jso.tex
add definition for proj distance and squintability

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{algorithm}
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\journal{Journal of Multivariate Analysis}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-num-names}
\usepackage{bookmark}

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, bottomrule=.15mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, breakable, toptitle=1mm, colframe=quarto-callout-note-color-frame, titlerule=0mm, opacityback=0, opacitybacktitle=0.6, coltitle=black, leftrule=.75mm, colback=white, arc=.35mm, bottomtitle=1mm, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, left=2mm]

@@

@@

Let \(A \in \mathbf{R}^{p \times d}\) be the d-D projection basis and
\(A^*\) be the optimal basis achieving the maximum index value for a
given projection pursuit problem defined by the shape to find, data
dimension, and the index function \(f(.)\). The projection distance
\(d(A, A^*)\), is defined as the Frobenius norm \(\lVert . \rVert _F\),
between the squared difference of these two bases:

\begin{equation}\phantomsection\label{eq-proj-dist}{d(A, A^*) = \lVert M \rVert _F = \sum_{ij} M_{ij}^2, \text{ where } M = AA^\prime - A^*A^{*\prime}\ .}\end{equation}

>>>>

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\theoremstyle{plain}
\newtheorem{assumption}{\protect\assumptionname}
\newtheorem{claim}{\protect\claimname}
\newtheorem{condition}{\protect\conditionname}
\newtheorem{conjecture}{\protect\conjecturename}
\newtheorem{cor}{\protect\corollaryname}
\newtheorem{defn}{\protect\definitionname}
\newtheorem{example}{\protect\examplename}
\newtheorem{lem}{\protect\lemmaname}
\newtheorem{notation}{\protect\notationname}
\newtheorem{problem}{\protect\problemname}
\newtheorem{prop}{\protect\propositionname}
\newtheorem{rem}{\protect\remarkname}
\newtheorem{thm}{\protect\theoremname}
\providecommand{\assumptionname}{Assumption}
\providecommand{\claimname}{Claim}
\providecommand{\conditionname}{Condition}
\providecommand{\conjecturename}{Conjecture}
\providecommand{\corollaryname}{Corollary}
\providecommand{\definitionname}{Definition}
\providecommand{\examplename}{Example}
\providecommand{\lemmaname}{Lemma}
\providecommand{\notationname}{Notation}
\providecommand{\problemname}{Problem}
\providecommand{\propositionname}{Proposition}
\providecommand{\remarkname}{Remark}
\providecommand{\theoremname}{Theorem}
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\journal{Journal of Multivariate Analysis}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-num-names}
\usepackage{bookmark}

@@

\begin{tcolorbox}[enhanced jigsaw, toptitle=1mm, bottomrule=.15mm, breakable, colbacktitle=quarto-callout-note-color!10!white, title={Algorithm: Jellyfish Optimizer Pseudo Code}, coltitle=black, colback=white, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, titlerule=0mm, arc=.35mm, opacityback=0, leftrule=.75mm, toprule=.15mm, opacitybacktitle=0.6, rightrule=.15mm, left=2mm]

@@

\begin{defn}\label{def:proj-dist}
Let $A \in \mathbf{R}^{p \times d}$ be the d-dimensional projection basis and
$A^*$ be the optimal basis that achieves the maximum index value for a given
PP problem defined by the shape to find, data dimension,
and the index function. The projection distance $d(A, A^*)$ between $A$ 
and $A^*$ is defined as 
$d(A, A^*) = \lVert AA^\prime - A^*A^{*\prime}\  \rVert _F$
where $\lVert . \rVert _F$ denotes the Frobenius norm, given by
$\lVert M \rVert _F = \sqrt{\sum_{ij} M_{ij}^2}$. 
\end{defn}

\begin{defn}\label{def:squintability}
Let $g$ be the function that maps the projection distance, $d = d(A, A^*)$, 
to the index value $f(XA)$, such that $g(d(A, A^*)) = f(XA)$.
The squintability of $f(\cdot)$, denoted $\varsigma(f)$, is defined as 
$$\varsigma(f) = c \times \max_{d} \Delta g(d) \times \arg \max_{d}  \Delta g(d)$$ 
where $c$ is a constant scaling factor, $\max_A \Delta g(x)$ represents the 
maximum change in the index value along the curve $g$, and $\arg \max_{d} \Delta g(x)$ represents the projection distance at which this largest gradient is attained.

\end{defn}

Definition \ref{def:squintability} is \ldots{}

@@
